Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-20 article.tex
Add refs what is known on selection

@@

\paragraph{MHC-I}

@@

@@

\richel{Check against stupidity}
Regarding human viruses, we do not know the extent to which the human
immune systems selects on these, nor which loci are selected
upon \richel{so I should read the literature on that}. 
We predict that there is a strong 
evolutionary conservation in regions that are essential for viral proteins'
functions. Because these regions are rare in a viral proteome,
and differ widely between pathogens, we expect that the human immune system
is not tailored to detect these sites. TMHs, however, have less 
functional constraints yet are more general. Because TMHs are more general,
we expect it for the immune system to pay off to be more attentive towards
TMHs. 
Additionally, viruses are not only selected for their evasion of an 
immune response, yet are selected to have a high reproductive value.
Because the strength of the evolutionary signal is unknown,
we use a strong data set to be able to detect it.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{pics/covid_genome_and_proteome.png}
  \caption{
    Overview of COVID-19 genome and proteome.
    From \url{https://zhanglab.ccmb.med.umich.edu/COVID-19}
  }
  \label{fig:covid_genome_and_proteome}
\end{figure}

@@

\begin{table}
  \input{mhc2_haplotypes.latex}
  \caption{
    Percentage of MHC-II haplotypes, from \cite{greenbaum2011functional}
    \richel{
      This is just a reminder, instead of new research. 
      This table be deleted in the future.
    }
  }
  \label{table:bbbq_2_percentages}
\end{table}

>>>>

% Just to have them already
% \begin{sloppypar}
% \end{sloppypar}

@@

\paragraph{MHC-I presents TMH-derived epitopes in humans more often}

@@

\paragraph{Does MHC-I present TMH-derived epitopes from pathogens as often?}

It is important that MHC-I presents both the polypeptides of the 
(healthy) cell, as well as possible pathogen-derived polypeptides when the
cell is infected. As described above, MHC-I presents TMH-derived epitopes 
from the human host more often. It is unknown if MHC-I has the same
dedication to present epitopes that stem from TMHs derived from
proteins produced by pathogen, either would the pathogen
be a virus \richel{$\mathcal{H}_{1,1}$} or 
a bacterium \richel{$\mathcal{H}_{1,2}$}.

@@

\richel{Check against stupidity}
Regarding human viruses, we do not know the selection pressure
exerted by the human immune system.
We do know that this selection pressure is 
limited for seasonal influenza \cite{han2019individual},
but this study does not show how frequent selected upon 
TMHs \richel{Use this study, if COVID-19 dataset is too weak}.
For COVID-19, there is preliminary evidence that the strongest
selection pressure is upon ORF3 (an ion channel and a viroporin)
and ORF8 (unknown function). ORF3 has 3 TMHs that appear irrelevant for
the natural selection of COVID-19.
We predict that evolutionary conservation is strongest 
for regions that are essential for viral proteins'
functions (such as catalytic binding sites), instead of TMHs.
Because these essential regions are rare in a viral proteome,
and differ widely between pathogens, we expect that the human immune system
is not tailored to detect these sites, similar to the aforementioned
influenza study. 
TMHs, however, have less 
functional constraints compared to catalytic regions,
and as such are more general. 
Because TMHs are more general,
we expect it for the immune system to pay off to be more attentive towards
TMHs. 
Additionally, viruses are not only selected for their evasion of an 
immune response, yet are selected to have a high reproductive value.
Because the strength of the evolutionary signal is unknown,
we use a strong data set to be able to detect it.

@@

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{pics/covid_genome_and_proteome.png}
  \caption{
    Overview of COVID-19 genome and proteome.
    From 
    \url{https://zhanglab.ccmb.med.umich.edu/COVID-19}
  }
  \label{fig:covid_genome_and_proteome}
\end{figure}

@@

\begin{table}
  \input{mhc2_haplotypes.latex}
  \caption{
    Percentage of MHC-II haplotypes, from \cite{greenbaum2011functional}
    \richel{
      This is just a reminder, instead of new research. 
      This table be deleted in the future.
    }
  }
  \label{table:mhc2_haplotypes}
\end{table}
